### 2013-02-05 doc/xps2013/proposal.tex
cbm

\item Our preliminary work has also revealed limitations of the current Grappa runtime system in the area of network scaling.  This proposal seeks funding to enhance the network layer and explore the architecture/software interactions of remote direct memory access (RDMA).

\item The size of data being processed by large systems today (hundreds of terabytes) dwarfs what can fit into a single system. Obviously multiple system nodes are required to maintain and access all of this data efficiently.  However, even with hundreds of channels to persistent storage, loading this data into DRAM can prove a bottleneck.  The Grappa runtime is designed to make applications tolerate extremely high memory latency, thus an idea we wish to explore is using solid state disks as main memory.

\item Presently there does not exist a comprehensive benchmark suite of irregular and graph applications.  We also seeking funding through this proposal to put together just such a

>>>>

\item Our preliminary work has also revealed limitations of the current Grappa runtime system with regards to network scaling.  This proposal seeks funding to enhance the network layer and explore the hardware/software interactions of remote direct memory access (RDMA).

\item The size of data being processed by large systems today (hundreds of terabytes) dwarfs what can fit into a single system. Multiple system nodes are required to maintain and access all of this data efficiently.  However, even with hundreds of channels to persistent storage, loading this data into DRAM can prove a bottleneck.  The Grappa runtime is designed to make applications tolerate extremely high memory latency, thus an idea we wish to explore is using solid state disks as main memory.

\item Presently there does not exist a comprehensive benchmark suite of irregular and graph applications.  We also seeking funding through this proposal to put together just such a benchmark suite.  This suite will include benchmarks, reference implementations, and input data-sets.  In addition a website will be created \texttt{graphbench.org} to distribute the benchmark suite and publish results.
